Dependent Object Types

### 2012-09-17 doc/fool/article.tex
ack viktor
field vs value consistency

Every field or type label can be declared only once in a set of
declarations $\seq D$. A set of declarations can hence be seen as a map from
labels to their declarations.  Meets $\wedge$ and joins $\vee$ on sets of
declarations are defined in ~\figref{dot-decls}.

@@

An alternative design would have been to change the expansion of the
function type to have a declaration for a special marker value label.

@@

We thank Amal Ahmed for many discussions and insights about applying
logical relations to DOT. We thank Donna Malayeri and Geoffrey
Washburn for preliminary work on DOT. We thank Tiark Rompf for helpful
comments.

>>>>

Every value, method or type label can be declared only once in a set of
declarations $\seq D$. A set of declarations can hence be seen as a map from
labels to their declarations.  Meets $\wedge$ and joins $\vee$ on sets of
declarations are defined in ~\figref{dot-decls}.

@@

An alternative design would have been to change the expansion of the
function type to have a declaration for a special label that either
prevents instantiation or requires an implementation for the
function.

@@

We thank Amal Ahmed for many discussions and insights about applying
logical relations to DOT. We thank Donna Malayeri and Geoffrey
Washburn for preliminary work on DOT. We thank Tiark Rompf and Viktor
Kuncak for helpful comments.
